Well-quasi-orderings on word languages

### 2025-10-16 src/conclusion.tex
fix: typos!

In some sense, our results confirm this intuition in the case of languages
described by a simple computational model. For languages recognized by
\kl{amalgamation systems}, being \kl{well-quasi-ordered} implies being a
\kl{bounded language}, and therefore being  included in some finite union of
languages of the form $w_1^* w_2 w_3^*$. Hence, these languages have at most a
quadratic \kl{factor complexity}. This is also the case for languages described
as the infixes of a finite set of pairs of \kl{morphic sequences}. Indeed, the
factor complexity of a \kl{morphic sequence} that is \kl{uniformly recurrent}
is linear \cite[Theorem 24]{NIPR09}, therefore the \kl{factor complexity} of a
language given by \kl{sequence representation} using \kl{morphic sequences} is
at most quadratic.

>>>>

In some sense, our results confirm this intuition in the case of languages
described by a simple computational model. For languages recognized by
\kl{amalgamation systems}, being \kl{well-quasi-ordered} implies being a
\kl{bounded language}, and therefore being  included in some finite union of
languages of the form $w_1^* w_2 w_3^*$. Hence, these languages have at most a
linear \kl{factor complexity}. This is also the case for languages described
as the infixes of a finite set of pairs of \kl{morphic sequences}. Indeed, the
factor complexity of a \kl{morphic sequence} that is \kl{uniformly recurrent}
is linear \cite[Theorem 24]{NIPR09}, therefore the \kl{factor complexity} of a
language given by \kl{sequence representation} using \kl{morphic sequences} is
at most linear.
